PragBat Models

### 2022-04-07 analysis/analysis.Rmd
update run

```{r}
library("papaja")
library(tidyverse)
library(knitr)
library(ggthemes)
library(corrr)
library(corrplot)
library(ggcorrplot)
library(reshape2)
library(coda)
#library(ggdist)
#library(psy)
#library(tidyboot)
#library(ggpubr)
#library(blavaan)
library(brms)

estimate_mode <- function(s) {
  d <- density(s)
  return(d$x[which.max(d$y)])
}

hdi_upper<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","upper"])
}

hdi_lower<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","lower"])
}
```
# Data

```{r}
data <- bind_rows(
  read_csv("../data/data_r1.csv") %>%filter(task != "training") %>%mutate(study = "study1"),
  read_csv("../data/data_r2.csv") %>%filter(task != "training")%>%mutate(study = "study2"),
  read_csv("../data/data_r3.csv") %>%filter(task != "training")%>%mutate(study = "study3")
  ) %>%
  mutate(study = factor(study),
         id = paste(study, id, sep = "_"),
         test_day = factor(test_day))
```

@@

ggsave(plot = prange,"../paper/figures/figure3.png", width = 4, height = 2.5, scale = 1.5)
```

# Reliability

```{r}
model_cor <- data_frame()

@@

```{r}
model <- 'prag  =~ ad_hoc_implicature + mutual_exclusivity + simple_inf
          card  =~ card_sorting
          match =~ match_to_sample'

model2 <- 'fac  =~ ad_hoc_implicature + mutual_exclusivity+ simple_inf + card_sorting + match_to_sample'

@@

```{r}
# fit <- bcfa(model, data = cfad, bcontrol = list(cores = 4), target = "stan", n.chains = 4, burnin = 5000, sample = 5000)
# saveRDS(fit, "../saves/bcfa_prag.rds")
fit <- readRDS("../saves/bcfa_prag.rds")

# fit2 <- bcfa(model2, data = cfad, bcontrol = list(cores = 4), target = "stan", n.chains = 4, burnin = 5000, sample = 5000)
# saveRDS(fit2, "../saves/bcfa_single.rds")
fit2 <- readRDS("../saves/bcfa_single.rds")

# fit3 <- bcfa(model3, data = cfad, bcontrol = list(cores = 4), target = "stan", n.chains = 4, burnin = 5000, sample = 5000)
# saveRDS(fit3, "../saves/bcfa_separate.rds")
fit3 <- readRDS("../saves/bcfa_separate.rds")

```{r}
bind_rows(
fitmeasures(fit)%>%as_tibble(rownames = "index")%>%
  mutate(model = "fit1"),
fitmeasures(fit2)%>%as_tibble(rownames = "index")%>%
  mutate(model = "fit2"),
fitmeasures(fit3)%>%as_tibble(rownames = "index")%>%
  mutate(model = "fit3")
)%>%
  write_csv("../saves/cfa_fit_measures.csv")

summary(fit2, fit.measures=TRUE, standardized = TRUE, rsquare = T)

blavInspect(fit, what = "postmean")%>%as_tibble(rownames = "index")%>%
  left_join(blavInspect(fit, what = "hpd")%>%as_tibble(rownames = "index"))%>%
  write_csv("../saves/cfa_estimates.csv")

@@

# RSA model

```{r}
rsa_model <- readRDS("../../../Spin-off/spin-off/model/output/model_pragBat3.rds")
```

```{r}
scale <- rsa_model %>%
  filter(parameter == "speaker_optimality",
         token == "scale_parameter")

pscale <- ggplot(scale, aes(x = value))+
  geom_density( alpha = 0.3, aes(fill = id), col = "black", adjust = 3)+
  geom_vline(xintercept = 1, lty = 2, col = "black", alpha = .75)+
  xlab("Scale parameter")+
  ylab("Density")+
  #facet_grid(~id, scale = "free_x")+
  theme_few()+
  scale_fill_viridis_d(name = "Task", labels = c("Informativeness inference", "Mutual exclusivity"))+
  theme(legend.position = c(.6,.7))
```

```{r}
so_est <- rsa_model %>%
  filter(parameter == "speaker_optimality",
         type == "subj_parameter",
         token == "speaker_optimality")%>%
  group_by(id)%>%
  summarise(mode = estimate_mode(value),
            uci = hdi_upper(value),
            lci = hdi_lower(value))

rsa <- data%>%
  filter(study == "study3", task == "card_sorting" | task == "match_to_sample")%>%
  group_by(id, task)%>%
  summarise(mean = mean(correct))%>%
  mutate(id = str_remove(id, "study3_"))%>%
  ungroup()%>%
  left_join(so_est)%>%
    mutate(task = recode(task,
                    `card_sorting` = "Card Sorting",
                    `match_to_sample` = "Relational Match-to-sample"))

cor <- rsa%>%
  group_by(task)%>%
  summarize(cor = round(cor.test(mean,mode)$estimate,2),
            lci =  round(cor.test(mean,mode)$conf.int[1],2),
            uci =  round(cor.test(mean,mode)$conf.int[2],2))%>%
  mutate(label = paste0("r = ", cor, " (",lci, " - ", uci,")"))

write_csv(cor, "../saves/rsa_cor_estimates.csv")

prsacor <- ggplot(rsa, aes(x = mean, y = mode))+
  #geom_abline(intercept = 2, slope = 1, lty = 2, alpha = .75)+
  geom_point(pch = 1, alpha = .75)+
  geom_smooth(method = "lm", col= "firebrick")+
  geom_text(data = cor, aes(label = label),y = 4.9, x = 0.2)+
  labs(x = "Mean proportion correct", y = "RSA model estimate (\u03b1)")+
  facet_grid(~task)+
  theme_few()

```{r}
rel_rsa_model <- readRDS("../../../Spin-off/spin-off/data/rsa_rel_est.rds")
```

```{r}
so_id_summary <- rel_rsa_model%>%
  group_by(day,id)%>%
  summarise(mode = estimate_mode(value),
            uci = hdi_upper(value),
            lci = hdi_lower(value))%>%
  pivot_wider(names_from = c(day), values_from = c(mode,uci,lci))

cor <- tibble(cor =  paste0(
  "r = ",
  round(cor.test(so_id_summary$mode_1, so_id_summary$mode_2)$estimate, 2),
  " (",
  round(cor.test(so_id_summary$mode_1, so_id_summary$mode_2)$conf.int[1], 2),
  " - ",
  round(cor.test(so_id_summary$mode_1, so_id_summary$mode_2)$conf.int[2], 2),
  ")"
  )
  )

prelrsa <- ggplot(so_id_summary, aes(x = mode_1, y = mode_2))+
  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 0.7, size = 0.5)+
  geom_errorbar(aes(ymin = lci_2, ymax = uci_2),width = 0, alpha = .5, col = "grey")+
  geom_errorbarh(aes(xmin = lci_1, xmax = uci_1), height = 0, alpha = .5, col = "grey")+
    geom_point(pch = 1, size = 2)+
    labs(x = "Day 1", y = "Day 2")+
  scale_y_continuous(limits=c(0,8),oob=squish)+
  #facet_grid(~chain)+
  geom_text(data = cor, aes(label =  cor), x = 0, y =7.5, hjust = 0)+
  #stat_cor(method = "pearson", aes(x = mode_1, y = mode_2), inherit.aes = F, size = 3)+
  theme_few()
```

```{r}
prsa <- ggarrange(
  prsacor,
  ggarrange(prelrsa, pscale, nrow = 2  , labels = c("", "C")),
  widths = c(3,1),
  labels = c("A", "B")
)

ggsave(plot = prsa,"../paper/figures/figure6.png", width = 10, height = 4, scale = 1.25)
```

>>>>

```{r}
library(tidyverse)
library(knitr)
library(ggthemes)
library(corrr)
library(corrplot)
library(ggcorrplot)
library(reshape2)
library(brms)
library(psy)
library(tidyboot)
library(ggpubr)
library(blavaan)
```

```{r}
data <- bind_rows(
  read_csv("../data/data_r1.csv") %>%filter(task != "training") %>%mutate(study = "study1"),
  read_csv("../data/data_r2.csv") %>%filter(task != "training")%>%mutate(study = "study2"),
  read_csv("../data/data_r3.csv") %>%filter(task != "training")%>%mutate(study = "study3")
  ) %>%
  mutate(study = factor(study),
         id = paste(study, id, sep = "_"))

data%>%
  group_by(task)%>%
  summarise(trials = length(unique(trial)))
```

@@

ggsave(plot = prange,"../paper/figures/figure3.png", width = 4, height = 2.5, scale = 1.5)
```
# Reliability
```{r}
model_cor <- data_frame()

@@

```{r}
model <- 'prag  =~ " mutual_exclusivity + ad_hoc_implicature + simple_inf
          card  =~ card_sorting
          match =~ match_to_sample'

model2 <- 'fac  =~ mutual_exclusivity + ad_hoc_implicature+ simple_inf + card_sorting + match_to_sample'

@@

```{r}
fit <- bcfa(model, data = cfad, bcontrol = list(cores = 4), target = "stan", n.chains = 4, burnin = 5000, sample = 5000)
saveRDS(fit, "../saves/bcfa_prag.rds")
fit <- readRDS("../saves/bcfa_prag.rds")

fit2 <- bcfa(model2, data = cfad, bcontrol = list(cores = 4), target = "stan", n.chains = 4, burnin = 5000, sample = 5000)
saveRDS(fit2, "../saves/bcfa_single.rds")
fit2 <- readRDS("../saves/bcfa_single.rds")

fit3 <- bcfa(model3, data = cfad, bcontrol = list(cores = 4), target = "stan", n.chains = 4, burnin = 5000, sample = 5000)
saveRDS(fit3, "../saves/bcfa_separate.rds")
fit3 <- readRDS("../saves/bcfa_separate.rds")
```

```{r}
fitmeasures(fit)%>%as_tibble(rownames = "index")

x <- summary(fit, fit.measures=TRUE, standardized = TRUE, rsquare = T)

blavInspect(fit, what = "postmean")%>%as_tibble(rownames = "index")%>%
  left_join(blavInspect(fit, what = "hpd")%>%as_tibble(rownames = "index"))

@@
